**COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata**

### 2023-03-24 manuscript_v2/02-methods.qmd
updating discussion

We used data from the *Survey of COVID-19 related Behaviours and Attitudes*, a repeated cross sectional survey focused on the Canadian province of Ontario that was commissioned by the Fields Institute for Research in Mathematical Sciences (henceforth Fields) and the  Mathematical Modelling of COVID-19 Task Force under ethical guidance from the University of Toronto. The survey collected socio-economic information from participants (@tbl-covariates), recorded their location (using the nearest municipality), and asked information on vaccination status by using the question "Have you received the first dose of the COVID vaccine?", with possible answers "yes" and "no". The original dataset contained 39,029 entries (where each entry corresponded to a unique respondent).

@@

Following an assessment of the number of entries corresponding to each Health Region in the final dataset, only 107 observations (4.3% of the total) corresponded to cities located in the North West and North East Health Regions. The low representation of these Health Regions in the dataset is noticeable in @fig-map,which shows that responses from these areas came from a relatively low number of cities when compared to the most populated Health Regions, such as the Toronto or Central Regions. We omitted the North East and North East Health Regions from further analyses due to the low number of entries. Therefore, the total number of unique entries used for analysis was 3,551 which included the East, Central, Toronto, and West Health Regions.

>>>>

We used data from the *Survey of COVID-19 related Behaviours and Attitudes*, a repeated cross sectional survey focused on the Canadian province of Ontario that was commissioned by the Fields Institute for Research in Mathematical Sciences (henceforth Fields) and the  Mathematical Modelling of COVID-19 Task Force under ethical guidance from the University of Toronto, and which ran between September 30th, 2021 and January 17th,2022. The survey collected socio-economic information from participants (@tbl-covariates), recorded their location (using the nearest municipality), and asked information on vaccination status by using the question "Have you received the first dose of the COVID vaccine?", with possible answers "yes" and "no". The original dataset contained 39,029 entries (where each entry corresponded to a unique respondent).

@@

Following an assessment of the number of entries corresponding to each Health Region in the final dataset, only 107 observations (4.3% of the total) corresponded to cities located in the North West and North East Health Regions. The low representation of these Health Regions in the dataset is noticeable in @fig-map,which shows that responses from these areas came from a relatively low number of cities when compared to the most populated Health Regions, such as the Toronto or Central Regions. We omitted the North East and North East Health Regions from further analyses due to the low number of entries. Therefore, the total number of unique entries used for analysis was 3,551 which included the East, Central, Toronto, and West Health Regions and that covered the period between September 30th,2021 and December 12th, 2021.

### 2023-03-24 manuscript_v2/04-discussion.qmd
updating discussion

The change from LHINs to Health Regions for healthcare in Ontario was aimed at reducing healthcare disparities [@tsasis2012]. The relatively recent nature of the change, which occurred in late 2019, highlights the importance of studies that can determine if there are intra-regional differences in healthcare that need to be addressed, particularly in the context of the COVID-19 pandemic.

Our results indicate that across the most densely populated Health Regions of Ontario, almost three quarters of the surveyed individuals reported having received the first dose of the COVID-19 vaccine (@tbl-descriptive-stats), and that there were no significant differences in vaccination odds among the age groups considered in the survey. This result is consistent with overall vaccination rates reported for Canada, which have been relatively higher when compared to other high income countries [@dube2022], with vaccination uptake rates across different age groups presented in other studies [@macdonald2021;@guay2022], and with the vaccination information provided by Public Health Ontario,  which shows that for the period where the Fields survey ran (Sept 30, 2021-Jan 17, 2022) there was a minimum of  80% of first dose vaccination coverage among all the age groups considered in the survey [@ontario-covid].

>>>>

There existence of healthcare disparities within Ontario is a topic of particular interest in due to the recent change in the healthcare system of this region, which eliminated the LHIN model and adopted larger Health Regions system in late 2019 in an attempt to address the disparities of the former approach [@tsasis2012;@dong2022]. In this context, analyzing COVID-19 vaccination estimates within the province is important as they can provide an initial assessment of variations that might need to be addressed by decision-makers.

Our results indicate that across the most densely populated Health Regions of Ontario, almost three quarters of the surveyed individuals reported having received the first dose of the COVID-19 vaccine (@tbl-descriptive-stats), and that there were no significant differences in vaccination odds among the age groups considered in the survey. This result is consistent with overall vaccination rates reported for Canada, which have been relatively higher when compared to other high income countries [@dube2022], with vaccination uptake rates across different age groups presented in other studies [@macdonald2021;@guay2022].

It is worth mentioning that the province-wide vaccination rate from the data for those 55 years of age and older, which was 72\%, can appear to be significantly lower from the vaccination rate reported for the same period by the public health agency of Ontario (Public Health Ontario), which reported a rate of 88.4\% at the start of the period covered by the data (September 30th, 2021 until December 12th, 2021) for those 50 years of age and older [@ontario-covid]. We believe the difference in this case can be explained by the fact that such province-wide estimates mask regional differences, which have been present in vaccination rates in the province since the start. This becomes apparent when vaccination rates are disaggregated by the Public Health Units in Ontario. For example, the Public Health Unit of Lambton (a region within the West Health Region) and the Public Health Unit of Haliburton, Kawartha, and the Pine Ridge District (an area covered by the East Health Region) both reported vaccination lower rates of 78\% for those 50 years of age and older at the beginning of the period of interest, whereas other regions  [@ontario-covid]. Moreover, differences in vaccination rates within the province continue as of today (late March of 2023), when, according to Public Health Ontario, some regions have less than 75\% vaccination rates [@ontario-covid-map].

age and older for the period covered by the data used for analysis in this study (late September of 2021 until mid-December of the same year) the vaccination rate provided by Public Health Ontario,  which shows that for the period where the Fields survey ran (Sept 30, 2021-Jan 17, 2022) there was a minimum of  80% of first dose vaccination coverage among all the age groups considered in the survey [@ontario-covid].

### 2023-03-24 manuscript_v2/appendix.qmd
updating discussion

clean_data <- read.csv(here("data","clean_dataset.csv"))

# remove rows with missing observations for race to obtain accurate numbers

clean_data<-clean_data %>% drop_na(race)
```

@@

```{r,ethnic information}
#| echo: false
#| warning: false
#| tbl-cap: Ethnic information from the clean dataset
  t6<-clean_data%>%
    select(race)%>%
    group_by(race)%>%
    summarise(observations = n()) %>%
  mutate(percentage = observations / sum(observations))%>%
    gt()%>%
      fmt_percent(
   columns=percentage,
    decimals=1)

@@

p2<-clean_data%>%
  select(age_group)%>%
   mutate(age_group_ord = fct_relevel(age_group,
                                      "16_24",
                                      "25_34",
                                      "35_44",
                                      "45_54",
                                      "55_64",
                                  "65_and_over"
                                          ))

  ggplot(p2%>%count(age_group_ord) %>%    # G count number in each group
         mutate(pct=n/sum(n),               # Calculate percent within each group
                ypos = 200),  # Calculate label positions
       aes(age_group_ord, n, fill=age_group_ord)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=paste0(sprintf("%1.1f", pct*100),"%"), y=ypos))+
  theme_classic()+
  thm1

@@

@@

#call scripts for data preparation and regression
source(here::here("code","data_preparation.R"))
source(here::here("code","regression.R"))

@@

clean_data %>% subset (Race=="white_caucasian")%>%
  tbl_summary(
    percent="row",
    by= first_dose,
    include=c(Health_Region),
    sort = all_categorical() ~ "frequency"
  ) %>% bold_labels()
```

@@

clean_data %>% subset (Health_Region=="West")%>%
tbl_summary(include=c(LHIN),
            sort = all_categorical() ~ "frequency") %>% 
  bold_labels()

>>>>

#call scripts for data preparation and regression
source(here::here("code","data_preparation.R"))
source(here::here("code","raking.R"))
source(here::here("code","regression.R"))
```

@@

```{r,ethnic information}
#| echo: false
#| warning: false
#| tbl-cap: Ethnic information from the clean dataset
  t6<-clean_data%>%
    select(Race)%>%
    group_by(Race)%>%
    summarise(observations = n()) %>%
  mutate(percentage = observations / sum(observations))%>%
    gt()%>%
      fmt_percent(
   columns=percentage,
    decimals=1)

@@

p2<-clean_data%>%
  select(Age_group)%>%
   mutate(Age_group_ord = fct_relevel(Age_group,
                                      "16_24",
                                      "25_34",
                                      "35_44",
                                      "45_54",
                                      "55_64",
                                  "65_and_over"
                                          ))

  ggplot(p2%>%count(Age_group_ord) %>%    # G count number in each group
         mutate(pct=n/sum(n),               # Calculate percent within each group
                ypos = 200),  # Calculate label positions
       aes(Age_group_ord, n, fill=Age_group_ord)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=paste0(sprintf("%1.1f", pct*100),"%"), y=ypos))+
  theme_classic()+
  thm1

@@

# Vaccination rates by Age

The table below provides the percentages of vaccination from the survey data.

```{r,vacc-table}
#| label: tbl-vaccination
#| tbl-cap: "Vaccination Status by Age from the Survey Data"
#| message: false
#| echo: false

clean_data$test<-as.factor(clean_data$age)

tvac<-clean_data %>%
  tbl_summary(percent="row",
              by= first_dose,
              include=test,
              label=test~"Age")%>%
  bold_labels()%>%
as_kable_extra(booktabs = TRUE,linesep="",longtable=T) %>%
  kableExtra::kable_styling(latex_options = "repeat_header")

tvac
```

@@

@@

clean_data %>% subset (Race=="white_caucasian")%>%
  tbl_summary(
    percent="row",
    by= first_dose,
    include=c(Health_Region),
    sort = all_categorical() ~ "frequency"
  ) %>% bold_labels()%>%
  as_kable_extra(booktabs = TRUE,linesep="")
```

@@

clean_data %>% subset (Health_Region=="West")%>%
tbl_summary(include=c(LHIN),
            sort = all_categorical() ~ "frequency") %>% 
  bold_labels()%>%
  as_kable_extra(booktabs = TRUE,linesep="")

### 2023-03-24 manuscript_v2/appendix.tex
updating discussion

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata},
  pdfauthor={Ariel Mundo Ortiz1; Bouchra Nasri2,},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

\begin{longtable}{lrr}
\caption{Ethnic information from the clean dataset}\tabularnewline

\toprule
race & observations & percentage \\ 
\midrule
arab\_middle\_eastern & 218 & $5.9\%$ \\ 
black & 306 & $8.3\%$ \\ 
east\_asian\_pacific\_islander & 308 & $8.3\%$ \\ 
indigenous & 216 & $5.8\%$ \\ 
latin\_american & 182 & $4.9\%$ \\ 
mixed & 324 & $8.7\%$ \\ 
other & 389 & $10.5\%$ \\ 
south\_asian & 383 & $10.3\%$ \\ 
white\_caucasian & 1383 & $37.3\%$ \\ 
\bottomrule
\end{longtable}

@@

@@

\hypertarget{tbl-hr-percentages}{}
\begin{longtable}[]{@{}lcc@{}}
\caption{\label{tbl-hr-percentages}Reported Vaccination Status from the
Survey for White/Caucasian Individuals by Health Region}\tabularnewline
\toprule()
\textbf{Characteristic} & \textbf{no}, N = 233 & \textbf{yes}, N =
1,080 \\
\midrule()
\endfirsthead
\toprule()
\textbf{Characteristic} & \textbf{no}, N = 233 & \textbf{yes}, N =
1,080 \\
\midrule()
\endhead
\textbf{Health\_Region} & & \\
Toronto & 85 (21\%) & 321 (79\%) \\
West & 69 (17\%) & 329 (83\%) \\
East & 41 (15\%) & 236 (85\%) \\
Central & 38 (16\%) & 194 (84\%) \\
\bottomrule()
\end{longtable}

\hypertarget{tbl-west-hr-lhin}{}
\begin{longtable}[]{@{}lc@{}}
\caption{\label{tbl-west-hr-lhin}Proportion of answers by LHIN (West
Health Region)}\tabularnewline
\toprule()
\textbf{Characteristic} & \textbf{N = 839} \\
\midrule()
\endfirsthead
\toprule()
\textbf{Characteristic} & \textbf{N = 839} \\
\midrule()
\endhead
\textbf{LHIN} & \\
Hamilton Niagara Haldimand Brant (Hnhb) & 271 (32\%) \\
Waterloo Wellington & 227 (27\%) \\
South West & 187 (22\%) \\
Erie St.~Clair & 154 (18\%) \\
\bottomrule()
\end{longtable}

>>>>

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata},
  pdfauthor={Ariel Mundo Ortiz1; Bouchra Nasri2,},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, boxrule=0pt, breakable, enhanced, frame hidden]}{\end{tcolorbox}}\fi

@@

\begin{longtable}{crr}
\caption{Ethnic information from the clean dataset}\tabularnewline

\toprule
Race & observations & percentage \\ 
\midrule
white\_caucasian & 1313 & $37.0\%$ \\ 
arab\_middle\_eastern & 214 & $6.0\%$ \\ 
black & 298 & $8.4\%$ \\ 
east\_asian\_pacific\_islander & 303 & $8.5\%$ \\ 
indigenous & 191 & $5.4\%$ \\ 
latin\_american & 180 & $5.1\%$ \\ 
mixed & 310 & $8.7\%$ \\ 
other & 367 & $10.3\%$ \\ 
south\_asian & 375 & $10.6\%$ \\ 
\bottomrule
\end{longtable}

@@

\hypertarget{vaccination-rates-by-age}{%
\section{Vaccination rates by Age}\label{vaccination-rates-by-age}}

The table below provides the percentages of vaccination from the survey
data.

\hypertarget{tbl-vaccination}{}
\begin{longtable}{lcc}
\caption{\label{tbl-vaccination}Vaccination Status by Age from the Survey Data }\tabularnewline

\toprule
\textbf{Characteristic} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,593\\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(continued)}}\\
\toprule
\textbf{Characteristic} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,593\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\textbf{Age} &  & \\
\hspace{1em}16 & 11 (21\%) & 41 (79\%)\\
\hspace{1em}17 & 15 (25\%) & 45 (75\%)\\
\hspace{1em}18 & 53 (36\%) & 93 (64\%)\\
\hspace{1em}19 & 33 (31\%) & 74 (69\%)\\
\hspace{1em}20 & 18 (17\%) & 85 (83\%)\\
\hspace{1em}21 & 30 (25\%) & 92 (75\%)\\
\hspace{1em}22 & 19 (23\%) & 62 (77\%)\\
\hspace{1em}23 & 21 (24\%) & 67 (76\%)\\
\hspace{1em}24 & 23 (29\%) & 55 (71\%)\\
\hspace{1em}25 & 25 (24\%) & 80 (76\%)\\
\hspace{1em}26 & 23 (30\%) & 53 (70\%)\\
\hspace{1em}27 & 16 (25\%) & 49 (75\%)\\
\hspace{1em}28 & 13 (20\%) & 52 (80\%)\\
\hspace{1em}29 & 13 (26\%) & 37 (74\%)\\
\hspace{1em}30 & 12 (21\%) & 44 (79\%)\\
\hspace{1em}31 & 17 (38\%) & 28 (62\%)\\
\hspace{1em}32 & 17 (27\%) & 47 (73\%)\\
\hspace{1em}33 & 17 (26\%) & 48 (74\%)\\
\hspace{1em}34 & 33 (35\%) & 60 (65\%)\\
\hspace{1em}35 & 31 (34\%) & 59 (66\%)\\
\hspace{1em}36 & 16 (25\%) & 49 (75\%)\\
\hspace{1em}37 & 15 (30\%) & 35 (70\%)\\
\hspace{1em}38 & 10 (28\%) & 26 (72\%)\\
\hspace{1em}39 & 5 (16\%) & 26 (84\%)\\
\hspace{1em}40 & 7 (16\%) & 36 (84\%)\\
\hspace{1em}41 & 5 (14\%) & 31 (86\%)\\
\hspace{1em}42 & 7 (19\%) & 30 (81\%)\\
\hspace{1em}43 & 9 (17\%) & 45 (83\%)\\
\hspace{1em}44 & 24 (33\%) & 48 (67\%)\\
\hspace{1em}45 & 23 (30\%) & 53 (70\%)\\
\hspace{1em}46 & 13 (24\%) & 41 (76\%)\\
\hspace{1em}47 & 18 (37\%) & 31 (63\%)\\
\hspace{1em}48 & 10 (33\%) & 20 (67\%)\\
\hspace{1em}49 & 8 (28\%) & 21 (72\%)\\
\hspace{1em}50 & 7 (16\%) & 38 (84\%)\\
\hspace{1em}51 & 7 (23\%) & 23 (77\%)\\
\hspace{1em}52 & 9 (20\%) & 36 (80\%)\\
\hspace{1em}53 & 9 (22\%) & 31 (78\%)\\
\hspace{1em}54 & 19 (37\%) & 33 (63\%)\\
\hspace{1em}55 & 12 (23\%) & 41 (77\%)\\
\hspace{1em}56 & 13 (26\%) & 37 (74\%)\\
\hspace{1em}57 & 12 (22\%) & 43 (78\%)\\
\hspace{1em}58 & 6 (14\%) & 38 (86\%)\\
\hspace{1em}59 & 4 (12\%) & 28 (88\%)\\
\hspace{1em}60 & 3 (11\%) & 25 (89\%)\\
\hspace{1em}61 & 1 (4.5\%) & 21 (95\%)\\
\hspace{1em}62 & 8 (26\%) & 23 (74\%)\\
\hspace{1em}63 & 5 (19\%) & 21 (81\%)\\
\hspace{1em}64 & 11 (33\%) & 22 (67\%)\\
\hspace{1em}65 & 11 (20\%) & 45 (80\%)\\
\hspace{1em}66 & 11 (28\%) & 28 (72\%)\\
\hspace{1em}67 & 8 (22\%) & 28 (78\%)\\
\hspace{1em}68 & 5 (19\%) & 21 (81\%)\\
\hspace{1em}69 & 17 (39\%) & 27 (61\%)\\
\hspace{1em}70 & 4 (14\%) & 24 (86\%)\\
\hspace{1em}71 & 1 (3.8\%) & 25 (96\%)\\
\hspace{1em}72 & 2 (9.1\%) & 20 (91\%)\\
\hspace{1em}73 & 3 (12\%) & 22 (88\%)\\
\hspace{1em}74 & 13 (31\%) & 29 (69\%)\\
\hspace{1em}98 & 147 (42\%) & 201 (58\%)\\*
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{longtable}

@@

\hypertarget{tbl-hr-percentages}{}
\begin{table}
\caption{\label{tbl-hr-percentages}Reported Vaccination Status from the Survey for White/Caucasian
Individuals by Health Region }\tabularnewline

\centering
\begin{tabular}{lcc}
\toprule
\textbf{Characteristic} & \textbf{no}, N = 233 & \textbf{yes}, N = 1,080\\
\midrule
\textbf{Health\_Region} &  & \\
\hspace{1em}Toronto & 85 (21\%) & 321 (79\%)\\
\hspace{1em}West & 69 (17\%) & 329 (83\%)\\
\hspace{1em}East & 41 (15\%) & 236 (85\%)\\
\hspace{1em}Central & 38 (16\%) & 194 (84\%)\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{tabular}
\end{table}

\hypertarget{tbl-west-hr-lhin}{}
\begin{table}
\caption{\label{tbl-west-hr-lhin}Proportion of answers by LHIN (West Health Region) }\tabularnewline

\centering
\begin{tabular}{lc}
\toprule
\textbf{Characteristic} & \textbf{N = 839}\\
\midrule
\textbf{LHIN} & \\
\hspace{1em}Hamilton Niagara Haldimand Brant (Hnhb) & 271 (32\%)\\
\hspace{1em}Waterloo Wellington & 227 (27\%)\\
\hspace{1em}South West & 187 (22\%)\\
\hspace{1em}Erie St. Clair & 154 (18\%)\\
\bottomrule
\multicolumn{2}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{tabular}
\end{table}

### 2023-03-24 manuscript_v2/main.qmd
updating discussion

library(weights)
library(here)
library(survey)
library(magrittr)
library(tidyverse)
library(lme4)
library(kableExtra)
library(modelsummary)
library(gtsummary)
library(patchwork)

```

>>>>

library(weights)
library(here)
library(survey)
library(magrittr)
library(tidyverse)
library(lme4)
library(kableExtra)
library(modelsummary)
library(gtsummary)
library(patchwork)
```
